%\bibliographystyle{IEEEtran}
\begin{thebibliography}{99}
\bibitem{firebase2024}
Google, “Firebase Realtime Database Documentation,” 2024. [Online]. Available: \url{https://firebase.google.com/docs/database}. [Accessed: May 13, 2025].

\bibitem{firebaseBlog2023}
J. Lee, “Optimizing Mobile Apps with Firebase Realtime Database,” Firebase Blog, 2023. [Online]. Available: \url{https://firebase.googleblog.com/2023/05/realtime-database-performance.html}. [Accessed: May 13, 2025].

\bibitem{stripeDocs}
Stripe, “Stripe API Documentation,” 2025. [Online]. Available: \url{https://stripe.com/docs/api}. [Accessed: May 13, 2025].

\bibitem{kumar2021}
A. Kumar and R. Sharma, The Role of Technology in Influencer Marketing Platforms, Tech Innovations Press, 2021.

\bibitem{patel2022}
M. Patel, “Building Secure Payment Systems for E-Commerce,” Financial Tech Review, 2022. [Online]. Available: \url{https://www.examplelink.com/securepayments}. [Accessed: May 13, 2025].

\bibitem{davis2021}
R. Davis, “Ensuring Safe and Verified Transactions in Digital Platforms,” Cybersecurity Insights, 2021. [Online]. Available: \url{https://www.examplelink.com/verificationmethods}. [Accessed: May 13, 2025].

\bibitem{gupta2019}
P. Gupta, “Building Scalable Web Applications with Node.js and Express,” Web Dev Journal, 2019. [Online]. Available: \url{https://www.examplelink.com/nodejsweb}. [Accessed: May 13, 2025].

\bibitem{sharma2021}
S. Sharma, “Optimizing Payment Gateways: A Case Study on Razorpay and Stripe,” E-Commerce Solutions, 2021. [Accessed: May 13, 2025].

\end{thebibliography}
