\chapter*{Acknowledgment}
\begin{justify}
I take this opportunity to express my heartfelt gratitude to all those who have contributed directly or indirectly to the successful completion of my project, \textbf{“INFLUENCIFY- A platform for brand collaborations and co-creations
”} Their support, guidance, and encouragement have been instrumental in every step of this journey.  

First and foremost, I would like to extend my deepest gratitude to the \textbf{Dr. Navin M. Upadhyay,(HOD CSE)}, for their unwavering support and for providing the infrastructure and academic resources that enabled this project to take shape. My sincere thanks also go to the \textbf{External Examiner} and \textbf{Internal Examiner}, whose invaluable feedback, constructive criticism, and insights refined the outcomes of this project and ensured its alignment with the required standards. I am equally grateful to the \textbf{Tech Support Team}, whose technical assistance, troubleshooting expertise, and consistent readiness to help proved indispensable during the implementation of the project.  

I owe a debt of gratitude to my dedicated \textbf{team members}, whose collaborative spirit, innovative ideas, and relentless efforts brought life to this endeavor. A special note of appreciation goes to my \textbf{friends}, whose moral support and encouragement kept me motivated even during challenging times. I am eternally thankful to my \textbf{parents}, who have been my constant pillars of strength, offering their unconditional love and support throughout my academic journey. Above all, I am grateful to the \textbf{Almighty}, whose blessings, guidance, and grace have been my source of inspiration and resilience. Last but not least, I extend my thanks to the \textbf{software tools, frameworks, and platforms} utilized in this project, and to everyone else who contributed, directly or indirectly, to the realization of this vision.  

To all the mentors, colleagues, and well-wishers who have been a part of this journey, your contributions have left an indelible mark on my work and personal growth. This acknowledgment is a token of my appreciation for your guidance and support in making \textbf{"INFLUENCIFY- A platform for brand collaborations and co-creations
"} a reality.  
\end{justify}
